% Content File: sections/forward_looking_statements.tex

\subsection{Cautionary Note Regarding Forward-Looking Statements}

This registration statement, including the sections on "Risk Factors," "Use of Proceeds," and "Acme Acquisition Corp.'s Business," contains forward-looking statements. These statements are based on the beliefs and assumptions of our management team and are subject to risks and uncertainties.

\replaced[id=JH]{Statements regarding future events or the future financial performance of the Company are examples of forward-looking statements.}{Such statements reflect our current views with respect to future events and are not guarantees.} You should not place undue reliance on these forward-looking statements.

\subsubsection*{Identifying Forward-Looking Statements}
All statements other than statements of historical fact contained in this registration statement are forward-looking statements. In some cases, you can identify forward-looking statements by terms such as "may," "will," "should," "expect," "plan," "anticipate," "could," "intend," "target," "project," "contemplate," "believe," "estimate," "predict," "potential," or "continue," or the negative of these terms or other similar expressions.

\subsection{Factors That Could Cause Actual Results to Differ}
\added[id=JW]{Actual results may differ materially from those indicated in the forward-looking statements.} Important factors that could cause actual results to differ materially include, but are not limited to: the ability to complete an initial business combination; the failure to realize the anticipated benefits of any business combination; and the continued loss of key personnel. We do not undertake any obligation to update these statements to reflect events or circumstances occurring after the date of this prospectus.
